Decades of ``group polarization'' replications may be undermined by high false discovery rates

### 2024-11-24 GroupPolarizationStatmod/paper/ms.tex
made figures and started writing analysis text

\mt{Graph with $\alpha(d^*)$ for $d^* = 0.2,~0.5,~0.8$ for each condition,
each article aggregated, and across all conditions/articles. Use color-coding for
each article, stems with dots at end, red to yellow gg2 theme, in order of
appearance.}

>>>>

We calculated the false detection rate across experimental conditions where
we identified parameters that generate spurious group polarization in the 
large-$N$ model (Figure~\ref{fig:fdr_experiments}). We then aggregated over
experimental conditions within each study to understand the false detection rate
across the ten studies (Figure~\ref{fig:fdr_studies}). Across the identified
spurious conditions, we calculated a mean false detection rate of 0.74 with
a significance level of $d^* = 0.5$. We also
examined the mean false detection rates across studies if we set a highly
optimistic estimate of the family-wise error rate, setting $\alpha = 0.05$. 
This only reduces the false discovery rate to 0.71, but does slightly change the
rankings of which study had the highest mean false discovery rates, with 
Schkade, et al., (2010) going from highest mean false discovery rate to 
second-lowest false discovery rate. The minimum false discovery rate in a study
was Myers (1975), with a false discovery rate of 0.58, meaning that probability
a group polarization detection in the best-designed study is greater than one in
two.
